### 2014-11-06 tex/results.tex
Did some minor clean-up with the results section.
Added table with performance numbers.

Hypothesis

\subsection{Implementation}

@@

\subsection{Evaluation} 
Experimental set-up

@@

Analysis

>>>>

Since the number of paths in GSE is exponential in the number of lazy initializations, it is expected that programs for which the number of lazy initializations is proportional to program complexity will evaluate more quickly using GSESH. On the other hand, since GSESH places a greater burden on the constraint solver, it is expected that programs where the lazy initialization count is constant or slowly increasing with respect to program complexity will evaluate more quickly using GSESH.

\subsection{JPF Implementation}
The Java Pathfinder (JPF) symbolic execution engine contains an implementation of GSE, which we extended with our own implementation of GSESH.

@@

\subsection{Evaluation} 
Experimental set-up: TO BE ADDED

@@

The results of the experiments are shown in table \ref{tab:results}.

\begin{table} [h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c | c | c |}
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
								&	&GSE	&SH	&GSE & SH\\
   \hline
    \multirow{3}{*}{LinkedList }&3	& 1 & 1  &1656 & 25		 \\
   		 				& 4	& 3 & 2	&17485  & 39 \\
   						& 5	& 20 & 3	&232743 & 56\\
						& 6	& 338 & 8		&3731094 & 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree }&1	& 0 & 1	& 4	 & 4\\
   		 				& 2	& 1 & 1 	& 26 & 17\\
   						& 3	& 12 & 7	& 305 & 118\\
    \hline
      \multirow{3}{*}{TreeMap}&1	& 0 & 1 	&9 & 9 \\
   		 				&2	& 1 & 3		& 100 & 46 \\
   						&3	&21 & 206	& 3026 & 547 \\

    \hline
  \end{tabular}
  \caption{test results}
  \label{tab:results}
\end{table}

\subsection{Analysis}

LinkedList
As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by GSE. By combining many of the GSE paths, SH avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.

BST
The BinarySearchTree example is somewhat of a mixed bag.

TreeMap
